---
title: "roxydoc"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


roxydoc2 is intended as a set of useful global tools for R package authors
to use when developing packages. It provides a series of wrapper and utility functions
aimed at supplementing the devtools and roxygen2 packages.

## Implementations
1) Set global author variables for package docs
2) Allow for flexible code creation, at the console or in a script with the 
   focus of documentation being the last thought
3) Properly format all latext and markdown output strings
4) Detailed data and output descriptions from actual code outputs
5) Addition of any copyright notices, or boilerplate to each script
6) Organization of code even when the author fights it...
7) Work at the console as much as you'd like, with script compiling running
   in the background


### Setting the global variables for the author 
```{r, fig.show='hold', comment=NA, echo=TRUE}
o <- lapply(list.files("R", pattern = "docr_", full.names=TRUE), source)
docr.defaults(author = "Joe Shmow", 
              email = "joe.s@emails.com", 
              company = "Joe's cRab shack", 
              website = "https://joeknowsr.com", 
              github = "JoeShmow")
```

This will then store the data to the .GlobalEnv as
```{r, eval=TRUE, comment=NA}
knitr::kable(docr.get_defaults())
```

So now when `docr.author` is called:
```{r, eval=TRUE, comment=NA,echo=TRUE}
docr.author()
```


### Documenting datasets

The primary purpose of R is generally to create, or manipulate raw data.
Often it is time consuming and tedious to properly format what the dataset
looks like, or contains. These functions aim to ease the burdon.

#### dataframes
```{r, eval=TRUE, comment=NA, fig.show='hold',echo=TRUE}
raw <- capture.output(docr.describe_df(df_in = mtcars, include_slice = TRUE))
cat(raw, sep = "\n")
```
#### lists
```{r, eval=TRUE, comment=NA, fig.show='hold',echo=TRUE}
raw2 <- capture.output(docr.list_named(as.list(sapply(as.list(mtcars),`[[`,1))))
cat(raw2, sep = "\n")
```


### And to add boilerplate to all files:
```{r, eval=TRUE, comment=NA, fig.show='hold',echo=TRUE}
cat(docr.meta_private(),sep = "\n")
```


### And writing code at the console and prepping for doc/scripts:
```{r, eval=TRUE, comment=NA, fig.show='hold',echo=TRUE}

docr.clean_fun <- function(fun_name = NULL, trim_blanks = FALSE,
                           rm_comments = FALSE, do_cat = TRUE){
  deparse(get(fun_name), control = "all") %>% (function(x){
    x[[1]] <- sprintf("%s <- %s",fun_name, x[[1]])

    if(trim_blanks){
      x <- x[nchar(x) > 0]
    }

    if(rm_comments){
      x <- grep("^[[:space:]]{1,}\\#", x, invert = TRUE, value = TRUE)
    }
    if(do_cat){
      cat(x, sep = "\n")
    }else {
      x
    }
  })
}
this.fun <- function(x = 1, y = 2,...){
    x * y
}
Fun <- docr.clean_fun('this.fun',do_cat = FALSE)
Args <- docr.param('this.fun')
Auth <- capture.output(docr.author())
Meta <- docr.meta_private()
cat(c(Meta,sprintf("#' %s",docr.fun('this.fun')),
      Args[[1]], sprintf("#' %s\n", Args[2:length(Args)]), Auth, Fun),sep = "\n")

```